%
% data collection form for structural testing
%

\subsection*{Subject identifier: \rule{3cm}{.5pt}}

\subsection*{Before beginning...}

\begin{enumerate}
\item How much experience have you had with C?

Experience (relative), please mark the scale appropriately, marks
between the boxes are OK: 

\begin{tabular}{|l||*{6}{p{1.4cm}|}}
\hline
Estimate& \centering 0  &  \centering 1 & \centering 2 & \centering 3 & \centering 4 &\ \ \ \  5 \\
\hline
\hline
Comparison  & none  & intro.  & lab    & part- & full-   & guru \\
            &       & course  & course & time  & time    &  \\
\hline
\end{tabular}

\item Experience (absolute), please enter:
Years: \underline{\ \ \ \ \ \ \ \ \ \ }

\item How motivated are you for the experiment?

\begin{tabular}{|l||*{6}{p{1.4cm}|}}
\hline
Estimate    & \centering 0 & \centering 1 & \centering 2 & \centering 3 & \centering 4 &\ \ \ \  5 \\
\hline
\hline
Comparison   & not at   & little & so-so  & pretty  & quite   & very \\
             & all      &        &        & much    & a bit   & much \\
\hline
\end{tabular}

\end{enumerate}

\subsection*{Results}

For all entries relating to elapsed time, please deduct the time you
took for breaks, meals, etc.

\begin{enumerate}
\addtocounter{enumi}{3}

\item When did you begin with the exercise in structural testing?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item How much time did you need at the beginning to construct test cases?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item Please enter here the name of the computer you used, as well as
the date and time when you began running your test cases: 
\rule{6cm}{.5pt} 

\item How many test cases did you end up constructing?
\rule{7mm}{.5pt} [count]

\item Please enter the coverage values which you attained with your
test cases (``fully satisfied''):
Binary branch \rule{7mm}{.5pt} [\%],
Switch \rule{7mm}{.5pt} [\%], 
Loop \rule{7mm}{.5pt} [\%], 
Operator Instrumentation \rule{7mm}{.5pt} [\%], 
Summary of all Condition Types \rule{7mm}{.5pt} [\%]

\item How much time did you need to type in, execute, and generate
additional test cases?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item When did you begin to search for failures?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item How much time did you need to search for failures?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item When did you begin to isolate faults?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item How much time did you need to isolate faults?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item When did you end the experiment?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item 
Please give your estimate of the per cent of faults that you found.
\rule{7mm}{.5pt} [per cent]

\item How well do you feel you've mastered structural testing?
Please mark the scale appropriately.

\begin{tabular}{|l||*{6}{p{1.4cm}|}}
\hline
Estimate& \centering 0  &  \centering 1 & \centering 2 & \centering 3 & \centering 4 &\ \ \ \  5 \\
\hline
\hline
Comparison  & not at& poorly  & could be& ok   & well    & super\\
            & all   &         & better &       &         &       \\
\hline
\end{tabular}

\end{enumerate}
