#
# Makefile for working with LaTeX documents (e.g., article).
# Supports dvi previewing, postscript previewing, bibtex, etc.
# This file supports a stub Makefile; the stub should use an "include" directive.
# 950202 Ch. Lott <lott@bellcore.com>
#
# Targets are:
#     make		- Generate the pdf file from the LaTeX source file.
#     make force	- Force regeneration of pdf file from the source
#			  (e.g., for second run to get table of contents)
#     make bbl		- Generate the bibliography from a BibTeX database.
#     make preview	- Generate and preview the dvi file using xdvi.
#     make pspreview	- Generate postscript version and preview that.
#     make ps2preview	- Generate postscript with 2 pages on 1 physical sheet
#			  and preview that. 
#     make print	- Print the dvi file on the specified laser printer.
#     make print2	- Like print, but 2 logical pages per physical page
#     make count	- Rough word count
#     make spell	- Check spelling of English documents.
#     make clean	- Remove all generated files.
#
# The name of the primary document and its dependencies should be
# entered in a file named "Makefile" in the appropriate directory.
# That stub Makefile file only needs to define these variables:
#	TEXDOC    (your latex source file)
#	DEPENDS   (any files used by your source file)
#	LATEX	  (latex, dlatex, latex2e, etc.)
# Then use the following line:
# 	include $HOME/..path../Makefile.latex

# The default typesetter.  Can also be overridden in the stub Makefile.
LATEX=pdflatex

# The default printer.  Can also be overridden in the stub Makefile.
PRINTER=ps1

DOCBASE = $(TEXDOC:%.tex=%)
PDFDOC  = $(DOCBASE).pdf
BBLDOC  = $(DOCBASE).bbl

# define a pattern for latex -> pdf files
%.pdf : %.tex
	$(LATEX) $<

# define a pattern for generating a .bbl file, which depends on the aux file.
# To keep this Makefile simple, depend on the dvi file (created with .aux)
%.bbl: %.dvi
	bibtex $*

# Default rule: make the .pdf file
# depends on the source file and all dependencies.
$(PDFDOC):   $(TEXDOC) $(DEPENDS)

# .bbl file depends on the .aux file, which depends on the source file
$(BBLDOC):	$(TEXDOC)

# if a bibliography must be made, format the document twice after doing so
bbl: $(BBLDOC)
	$(LATEX)  $(TEXDOC)
	$(LATEX)  $(TEXDOC)

# force a reformat of the source file
force:
	$(LATEX) $(TEXDOC)

# how long is the document
count:
	@echo "counting words in document $(TEXDOC)."
	detex $(TEXDOC) | wc -w

# check the spelling in the source file; only works for English
spell:  
	@if [ ! -f spell-words ]; then \
		echo ""; \
		echo -n "NOTE:  To create a file with the following "; \
		echo "list of words in it, ";\
		echo -n "type 'make spell-words'   "; \
		echo "(An empty file was created for you.)";\
		echo ""; \
		touch spell-words; \
	fi
	detex $(TEXDOC) | spell | comm -23 - spell-words

# build the file with the words that should not be reported as spelling errors
# e.g., s
spell-words: $(TEXDOC)
	detex $(TEXDOC) | spell | tee spell-words

# remove all output files that can be recreated from $(TEXDOC)
clean:
	rm -f $(PDFDOC) $(DOCBASE).aux $(DOCBASE).log

clobber: clean

# Additional dependencies in the following form:
#
#    product: source
