%
% data collection form for functional testing
%

\subsection*{Subject identifier: \rule{3cm}{.5pt}}

\subsection*{Before beginning...}

\begin{enumerate}
\item How much experience have you had with C?

Experience (relative), please mark the scale appropriately, marks
between the boxes are OK: 

\begin{tabular}{|l||*{6}{p{1.4cm}|}}
\hline
Estimate& \centering 0  &  \centering 1 & \centering 2 & \centering 3 & \centering 4 &\ \ \ \  5 \\
\hline
\hline
Comparison  & none  & intro.  & lab    & part- & full-   & guru \\
            &       & course  & course & time  & time    & \\
\hline
\end{tabular}

\item Experience (absolute), please enter:
Years: \underline{\ \ \ \ \ \ \ \ \ \ }


\item How motivated are you for the experiment?

\begin{tabular}{|l||*{6}{p{1.4cm}|}}
\hline
Estimate    & \centering 0 & \centering 1 & \centering 2 & \centering 3 & \centering 4 &\ \ \ \  5 \\
\hline
\hline
Comparison   & not at   & little & so-so  & pretty  & quite   & very \\
             & all      &        &        & much    & a bit   & much \\
\hline
\end{tabular}

\end{enumerate}

\subsection*{Results}

For all entries relating to elapsed time, please deduct the time you
took for breaks, meals, etc.

\begin{enumerate}
\addtocounter{enumi}{3}

\item When did you begin with the exercise in functional testing?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item How many equivalence classes did you produce?
\rule{7mm}{.5pt} [count]

\item Did you use equivalence class partitioning, boundary value
analysis, or both? [neither, ECP, BVA, both]

\item How many test cases did you write?
\rule{7mm}{.5pt} [count]

\item How much time did you need to construct the test cases?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item Please enter here the name of the computer you used, as well as
the date and time when you began running your test cases:
\rule{6cm}{.5pt} 

\item How much time did you need to type in and execute the test cases?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item When did you begin to search for failures?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item How much time did you need to search for failures?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item When did you begin to isolate faults?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item How much time did you need to isolate faults?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hours:minutes]

\item When did you end the experiment?
\rule{7mm}{.5pt} : \rule{7mm}{.5pt} [hour:minute]

\item Would you say that you found all of the faults?
Please give your estimate of the per cent of faults that you found.
\rule{7mm}{.5pt} [per cent]

\item How well do you feel you've mastered functional testing?
Please mark the scale appropriately.

\begin{tabular}{|l||*{6}{p{1.4cm}|}}
\hline
Estimate& \centering 0  &  \centering 1 & \centering 2 & \centering 3 & \centering 4 &\ \ \ \  5 \\
\hline
\hline
Comparison  & not at& poorly  & could be& ok   & well    & super\\
            & all   &         & better &       &         &       \\
\hline
\end{tabular}

\end{enumerate}
