
This is the supplemental sheet 
for applying technique ``structural testing''
to the program ``ntree.'' 

\bigskip

This exercise primarily tests several C functions.
To save you time and effort in this exercise, a test scaffold was
created. 
The driver functions required for this scaffold are in the precompiled
file ``driver.o'' and are bound in at link time.
The drivers take care of function such as testing for and opening
input files, allocating necessary memory, etc.  See also the notes
about one visible driver function that appear below.

\subsection*{Necessary inputs}

\begin{itemize}

\item Which documents belong to this exercise?

\begin{enumerate}
\item Document ES7, the specification of the component, which you will
receive after you have created test cases and attempted to reach 100\%
coverage.
\item Document EQ7, the source code of the component
\end{enumerate}

\item How do I fetch the files which I need?

Do the following:

\begin{enumerate}

\item First create a new directory for this exercise with the
``mkdir'' command.
\begin{verbatim}
    mkdir st-ntree
\end{verbatim}

\item Then change to the new directory with the ``cd'' command.
\begin{verbatim}
    cd st-ntree
\end{verbatim}

\item Finally, enter the following command:
\begin{path}
\begin{verbatim}
    tar xf ~prakt00/Exercise5/st-ntree.tar
\end{verbatim}
\end{path}

\end{enumerate}

\item What should I have?

The following files must be available:
\begin{verbatim}
    Makefile     gct-map     ntree     run-suite    test-dir
\end{verbatim}

\end{itemize}


\subsubsection*{Writing test cases}

All of the program's functions are fundamentally tested via the
invocation 
\begin{verbatim}
ntree <input file>
\end{verbatim}
A parameter file holds only the name of the input file.
This is somewhat awkward, but necessary to allow applying 
the test driver consistently.
The format of the input file is as follows:
\begin{verbatim}
command1 parameter1 paramter2
command2 paramterX
...
\end{verbatim}

Which commands are allowed in the input and which functions are
invoked by those commands can be seen in the function 
{\tt fuehre\_kommandos\_aus} in the file {\tt ntree.c}.
Because this function belongs to the test scaffold and will not
be part of the eventual application, it is not especially robust.
You can assume that the function, although sensitive, is free of
faults. 
One activity of the driver from {\tt driver.o} is to open the first
file on the command line and to invoke the function {\tt
fuehre\_kommandos\_aus} with a pointer to the opened file.
Don't write any test cases to cover the test scaffold!

\subsection*{Reminder}

Make sure that your test cases generate output so that you can
detect failures!

\subsection*{Brief description of the library functions used}

\begin{itemize}

\item {\tt assert(expression)}

Macro that expects the expression to be true at the time the
program is executed and in that case does nothing.  Otherwise an error
message with the expression is printed and the program is ended.

\item {\tt char* malloc(unsigned size)}

Returns a pointer to a block of memory that is at least as large as
{\tt size} bytes.  In case of failure, NULL is returned.

\item {\tt int free(ptr)}

Gives a previously allocated block back to the system.  
{\tt ptr} must have been allocated using {\tt malloc} or a similar
function.  If successful, 1 is returned; otherwise 0 is returned.

\item {\tt int strcmp(s1,s2)}

Compares two strings.  Returns a value greater than, equal to, or less
than 0 depending on whether {\tt st1} is lexicographically (i.e.,
ASCII value) greater than, equal, or less than {\tt s2}.

\item {\tt void bcopy(b1,b2,length)}

Copies {\tt length} bytes from string {\tt b1} to string {\tt b2}.
Overlapping strings are treated correctly.

\item {\tt int sscanf(s,format,pointer)}

Reads characters from string {\tt s}, converts them according to
the specification string {\tt format}, and writes the result into
the variables pointed to by the {\tt pointer}s.
This is the reverse function of {\tt printf}; the format specification
strings are identical.

\item {\tt char *fgets(s,n,stream)}

Reads characters from the stream {\tt stream} and writes them in the
string {\tt s}, until either {\tt n-1} characters have been read or
one of NEWLINE or EOF are seen.
At EOF the value NULL is returned, otherwise {\tt s}.

\item {\tt char *strdup(s1)}

Duplicates the string {\tt s1}.  Allocates memory for this purpose
using {\tt malloc()} and returns a pointer to the duplicate if
successful, otherwise NULL.

\end{itemize}
