%
% faults in nametbl
%

The classification of each fault is given in braces.

\begin{enumerate}

% 1
\item Fault in file ``nametbl.h'', line 7:  The constants ``FUNCTION''
and ``DATA'' are swapped.

\{Comission, Data\}

Causes failure: If the resource type of a symbols is entered with the
command ``trt'' to be ``FUNCTION,'' then the symbol is prointed as
having the type ``DATA''.

% 2
\item Fault in function ``insert\_entry'', line 61: The variable {\tt
numitems} is not incremented.

\{Omission, Computation\}

Causes failure: The count of entries in the print-out of the symbol
tables does not reflect how many elements were inserted (remains 0).

% 3
\item Fault in function ``setObjType'', line 94: The variable ``new\_ot'' 
is not stored.

\{Omission, Data\}

Causes failure: The value for the object type is not stored; only the
default value appears in the output (``OT\_NO\_INF'').

% 4 
\item Fault in function ``setResType'', line 108/111: The curly
brackets are missing.

\{Omission, Control\}

Causes failure: If a node is not found, the null pointer is
dereferenced (written) and causes (in most cases) a core dump.

% 5 
\item Fault in function ``ins'', line 124: The last parameter in the
function call is missing.

\{Omission, Interface\}

Causes no failure.  The field for the resource type receives a 
random value (apparently null when gcc is used, which reflects the
encoding of the value ``FUNCTION'').

% 6
\item Fault in function ``ins'', line 128: The word ``Tabelle'' is
written without the ``a''.

\{Commission, Cosmetic\}

Causes failure: A misspelled word appears in the output.


% 7 
\item Fault in function ``trt'', line 177: The enumerated type value
"FUNCTION'' was written with a ``K'' instead of a C.

\{Commission, Control\}

Causes failure: The resource type is not recognized.

% 8 
\item Fault in function ``sch'', line 205: missing error message.

\{Omission, Control\}

Causes failure: No error message is printed if the name is not found.

\end{enumerate}

Comments:
\begin{enumerate}
\item Lines 144/173: The tests for  OT\_NO\_INF und RT\_NO\_INF are
superfluous according to the specification, but this is not considered
a fault.
\end{enumerate}
