%
% list of faults in code object count
%

The classification of each fault is given in braces.

\begin{enumerate}

\item Fault in line 10: 
The variables are initialized with 1, should be with 0.

\{Comission, Initialization\}

Causes failure:
The sums are incorrect (off by one).

\item Fault in line 14: 
The variable ``fp'' is not initialized in the case that the input 
should be taken from ``stdin''.

\{Omission, Initialization\} 

Causes failure:
The program cannot read from stdin.


\item Fault in line 15: 
The invocation of fprintf uses ``stdout'' instead of ``stderr''.

\{Comission, Interface\} 

Causes failure:
Error messages appear on the standard output (stdout) instead of the
standard-error output (stderr).


\item Fault in line 16: 
Component is terminated with ``exit (1)'', where ``continue'' should
have been used.

\{Comission, Control\}

Causes failure:
If a file is not found, the program stops there instead of continuing
on to other files; also, no sum is printed.


\item Fault in line 19: 
The variable ``inword'' is initialized with 1 instead of 0.

 \{Comission, Initialization\}

Causes failure:
Depending on whether the first symbol in a file is whitespace, the
program reports that files with n words have either n or n - 1 words.


\item Fault in line 34: *argv is used instead of argv[i].

\{Comission, Data\}

Causes failure:
The program prints its own name instead of the file name when
reporting the counts.


\item Fault in line 41: Argc is compared with 1, but should be
compared with 2.

\{Comission, Computation\}

Causes failure:
The program prints out sums even when only a single file was
processed.


\item Fault in line 42: Instead of ``tlinect'' the variable ``linect'
is used.

\{Comission, Data\}

Causes failure:
The sums are not computed correctly.  Example:
{\small
\begin{verbatim}
% ./count file2 file2 file2
      1       2      14 ./count
      1       2      14 ./count
      1       2      14 ./count
      1       7      43 total
\end{verbatim}
}
\end{enumerate}


