
This is the supplemental sheet 
for applying technique ``functional testing''
to the program ``cmdline.'' 

\subsection*{Necessary inputs}

\begin{itemize}

\item Which documents belong to this exercise?

\begin{enumerate}
\item Document ES8, the specification of the component
\item Document EQ8, the source code of the component, which you will
receive after you have written test cases and diagnosed failures.
\end{enumerate}

\item How do I fetch the files which I need?

Do the following:

\begin{enumerate}

\item First create a new directory for this exercise with the
``mkdir'' command.
\begin{verbatim}
    mkdir ft-cmdline
\end{verbatim}

\item Then change to the new directory with the ``cd'' command.
\begin{verbatim}
    cd ft-cmdline
\end{verbatim}

\item Finally, enter the following command:
\begin{path}
\begin{verbatim}
    tar xf ~prakt00/Exercise5/ft-cmdline.tar
\end{verbatim}
\end{path}

\end{enumerate}


\item What should I have?

The following files must be available.
\begin{verbatim}
    Makefile        cmdline         run-suite       test-dir
\end{verbatim}

\end{itemize}

\subsection*{Creating equivalence classes and test cases}

The component ``cmdline'' can almost be tested directly.
The arguments for the individual invocations of ``cmdline'
must still be saved in parameter files.
No MIL/MDL input files are required.

\newpage
\noindent {\Large\bf Document E28, part 2: To be given out with the code!}

\subsection*{Brief description of the library functions used}

\begin{itemize}

\item {\tt int strlen(char *s)}

Returns the length of the string {\tt s} (the null character on the end
is not counted).

\item {\tt int strcmp(char *s1, char *s2)}

Compares two strings.  Returns a value greater than, equal to, or less
than 0 depending on whether {\tt st1} is lexicographically (i.e.,
ASCII value) greater than, equal, or less than {\tt s2}.

\item {\tt int strncmp(char *s1, char *s2, int n)}

Like {\tt strcmp}, but compares maximum {\tt n} characters.

\item {\tt int fprintf(stderr, "Text"...)}

Prints the text on the standard-error output stream.

\item {\tt int isdigit(char c)}
Returns {\em true} if the character is a digit, otherwise {\em false}.

\item {\tt int atoi(char *str)}

Converts the string {\tt str} to an integer.
Leading white space is ignored, and scanning of the string ends
with the first non-numeric character.
If no numeric characters could be read, 0 is returned.

\end{itemize}

